Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2023-02-06 RR_manuscript/RR.tex
🐛 - re-apply changes from bd13382ce5927a554babf2561c739db5a915c13a (fixes #319)

When considering both acoustic and statistical analyses, we have found a grand total of 119 different analytic pipelines.
In other words, each individual analysis submitted was unique.

@@

While one might find it obvious that measuring different parts of the speech signal can lead to different results, the fact that analysts (and reviewer alike) considered all these data analytic pipelines valid ways of answering the same research question points to a lack of theoretical consensus on what parts of the speech signal correspond to what types of communicative functions.
Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates:
For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations.
While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, mininum, maximum, or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
As shown by Breznau et al. \citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.

>>>>

When considering both acoustic and statistical analyses, we have found a grand total of 119 different analytic pipelines.
In other words, each individual analysis submitted was unique.
A sankey diagram illustrating the relationship between choices related to outcome, temporal window and operationalization can be found in the supplementary materials at \url{https://many-speech-analyses.github.io/many_analyses/RR_manuscript/supplementary_materials.pdf}.

@@

While one might find it obvious that measuring different parts of the speech signal can lead to different results, the fact that analysts (and reviewer alike) considered all these data analytic pipelines valid ways of answering the same research question points to a lack of theoretical consensus on what parts of the speech signal correspond to what types of communicative functions.
Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates:
For example, five teams measured f0 in the noun and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.35 to 0.19 standard deviations.
While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, minimum, maximum, point or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-2 and the number of random effect terms ranged from 1-10).
As shown by Breznau et al. \citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
